Cycle Route Uptake and Scenario Estimation (CRUSE): an approach for developing strategic cycle network planning tools

### 2024-04-17 paper.qmd
Tidyverse
Add more details
Minor updates

@@

@@

```{r}
#| include: false
library(tidyverse)
```

@@

```{r alternative}
#| fig-cap: Hypothetical user stories for the CRUSE Tool illustrating that it can be used in different ways by different user groups.
#| label: fig-user-stories
schematic = DiagrammeR::grViz("
digraph {
  # graph statement
  #################
  graph [rankdir = LR
         color = white
         fontsize = 36]

  # nodes (rectangles)
  #################
   node [shape = rectangle            
       margin = 0.4
       fontsize = 36
       fixedsize = false
       width = 1]

   subgraph cluster_2 {
     graph[shape = rectangle]
         C2b [label = 'Exploration']
         C2a [label = 'CRUSE\ncounty level results']
         C2 [label = 'CRUSE\nnational map']
         B2 [label = 'CRUSE\nlanding page']
         A2 [label = 'Non-professional\nuser'] 
}

   subgraph cluster_1 {
   graph[shape = rectangle]
         Dd [label = 'Data dowloads']
         Dc [label = 'Quiet and fast route\nnetworks']
         Db [label = 'County statistics']
         Da [label = 'Full county map']
         D [label = 'CRUSE\ncounty map']
         C [label = 'CRUSE\nnational map']
         B [label = 'CRUSE\nlanding page']
         A [label = 'Professional user'] 
}

  # node (triangle)
  #################
  node [shape = diamond]
         Dd1 [label = 'External\ntools']
         C2b1 [label = 'Communication']
  # edges 
  #######
  A2 -> B2
  A -> B
  B -> C
  B2 -> C2
  C -> D
  C2 -> C2a
  C2 -> C2b
  C2a -> C2b
  C2b -> C2b1
  D -> Da 
  D -> Db 
  D -> Dc 
  D -> Dd 
  Dd -> Dd1

}
")
# schematic
# htmlwidgets::saveWidget(schematic, "images/fig5.html")
# browseURL("images/fig5.html")
# webshot2::webshot(url = "images/fig5.html", file = "images/fig5.png")
# knitr::include_graphics("images/fig5.png")
schematic
```

>>>>

<details>

@@

This is an open and reproducible paper. See [github.com/cruse-bike](https://github.com/cruse-bike) for the code and data used to generate the results presented here, and the code underlying the web app hosted at [cruse.bike](https://cruse.bike/).

</details>

@@

```{r}
#| include: false
library(readr)
library(dplyr)
```

@@

```{r alternative}
#| fig-cap: Hypothetical user stories for the CRUSE Tool illustrating that it can be used in different ways by different user groups.
#| label: fig-user-stories
# schematic = DiagrammeR::grViz("
# digraph {
#   # graph statement
#   #################
#   graph [rankdir = LR
#          color = white
#          fontsize = 36]

#   # nodes (rectangles)
#   #################
#    node [shape = rectangle            
#        margin = 0.4
#        fontsize = 36
#        fixedsize = false
#        width = 1]

#    subgraph cluster_2 {
#      graph[shape = rectangle]
#          C2b [label = 'Exploration']
#          C2a [label = 'CRUSE\ncounty level results']
#          C2 [label = 'CRUSE\nnational map']
#          B2 [label = 'CRUSE\nlanding page']
#          A2 [label = 'Non-professional\nuser'] 
# }

#    subgraph cluster_1 {
#    graph[shape = rectangle]
#          Dd [label = 'Data dowloads']
#          Dc [label = 'Quiet and fast route\nnetworks']
#          Db [label = 'County statistics']
#          Da [label = 'Full county map']
#          D [label = 'CRUSE\ncounty map']
#          C [label = 'CRUSE\nnational map']
#          B [label = 'CRUSE\nlanding page']
#          A [label = 'Professional user'] 
# }

#   # node (triangle)
#   #################
#   node [shape = diamond]
#          Dd1 [label = 'External\ntools']
#          C2b1 [label = 'Communication']
#   # edges 
#   #######
#   A2 -> B2
#   A -> B
#   B -> C
#   B2 -> C2
#   C -> D
#   C2 -> C2a
#   C2 -> C2b
#   C2a -> C2b
#   C2b -> C2b1
#   D -> Da 
#   D -> Db 
#   D -> Dc 
#   D -> Dd 
#   Dd -> Dd1

# }
# ")
# schematic
# htmlwidgets::saveWidget(schematic, "images/fig5.html")
# browseURL("images/fig5.html")
# webshot2::webshot(url = "images/fig5.html", file = "images/fig5.png")
knitr::include_graphics("images/fig5.png")
```
